Declarative Data Analytic

### 2015-05-27 paper.tex
Add questions

\section{Summary for \saf}
\label{sec:saf}

@@

@@

@@

>>>>

\section{\saf}
\label{sec:saf}

@@

\paragraph{Progress.}

@@

\paragraph{Questions:}

\begin{itemize}
\item Are GISP\_Original, Thin\_client\_environment and Tamagawa related data? 
\item Do all of them contain anomalies? 
\item What has been done to diagnose/solve the anomalies, if any?

\end{itemize}

@@

\section{Project}
\label{sec:project}

\subsection{Goal}
\label{sec:proj:goal}
Help the user to define failure models of systems, so that the failure model
could help identify the root cause of anomalies.
